This code analyzes the preprocessed data.
Specifically, it analyzes the Wordcount, informativeness, readability, valence, time, and AX measurements.
The self-disclosure measure is performed in the "analyze_object_analysis.Rmd"

```{r}
library('tidyverse')
library("readxl")

```
```{r}
# Load the data
# Traditional Survey
data_A <- read_excel("D:\\VU\\Validators\\Data\\preproc_data_A.xlsx")
# Chatbot-typed
data_B <- read_excel("D:\\VU\\Validators\\Data\\preproc_data_B.xlsx")
# Chatbot-spoken
data_C <- read_excel("D:\\VU\\Validators\\Data\\preproc_data_C.xlsx")

conditions = c('A','B','C')

```
Create dataframe for each variable, questions and condition
```{r}

# Return a dataframe for the requested variable
make_df <- function(data, condition, cur_var){
    # Check for which data needs to be extracted
    # Wordcount
    if(cur_var == 'wc'){
      df = data.frame(wc1 = data$wc_inzet,
                           wc2 = data$wc_org,
                           wc3 = data$wc_pers,
                           wc4 = data$wc_intent,
                           wc5 = data$wc_disclosure)
    # informativeness  
    } else if (cur_var == 'inf'){
      df = data.frame(inf1 = data$inf_inzet,
                         inf2 = data$inf_org,
                         inf3 = data$inf_pers,
                         inf4 = data$inf_intent,
                         inf5 = data$inf_disclosure)
    # Readability  
    } else if (cur_var == 'read'){
      df = data.frame(read1 = data$read_inzet,
                           read2 = data$read_org,
                           read3 = data$read_pers,
                           read4 = data$read_intent,
                           read5 = data$read_disclosure)
    # Binary emotional score
    } else if (cur_var == 'emo'){
      df = data.frame(e1 = data$e_inzet,
                           e2 = data$e_org,
                           e3 = data$e_pers,
                           e4 = data$e_intent,
                           e5 = data$e_disclosure)
    # Percentual Valence Score
    } else if (cur_var == 'val'){
      df = data.frame(val1 = data$val_inzet,
                           val2 = data$val_org,
                           val3 = data$val_pers,
                           val4 = data$val_intent,
                           val5 = data$val_disclosure)
    # Demographic
    } else if (cur_var == 'demo'){
      df = data.frame(dem_age = data$age,
                          dem_gender = data$gender,
                          dem_edu = data$edu)
    # Time
    } else if (cur_var == 'time'){
      df = data.frame(t1 = data$time1, 
                           t2 = data$time2,
                           t3 = data$time3,
                           ts = data$subj_time)
    # User Experience
    } else if (cur_var == 'ux'){
      df = data.frame(telang = data$ux_telang,
                         formulering = data$ux_formulering,
                         saai = data$ux_saai,
                         intuitief = data$ux_intuitief,
                         verwarrend = data$ux_verwarrend,
                         nadenken = data$ux_nadenken,
                         verkies = data$ux_verkies,
                         cb_ervaring = data$ux_chatbot_ervaring,
                         cb_survey = data$ux_chatbot_survey)
    }else{
      warning('unknown cur var')
    }

    # Extra processing for condition C answers, remove empty cells
    C_vars = c('wc','inf','read','val', 'emo')
    if (condition == 'C' & (cur_var %in% C_vars)){
        find_empty_cells <- function(x){
          ex_index <- unique(-c(which(is.na(x)), 
                                which(x == '0'), 
                                which(x == 0)))
          return (ex_index)
        }
      # go through the answer of each question
      na_in_empty_cells <- function(df_x){
        for (i in c(1:5)){
          na_row = get(paste('ex_q',i,sep = ''))
          df_x[-na_row,i] <- NaN
        }
        return (df_x)
      }
      
      # Find all empty answers for the questions
      ex_q1 <- find_empty_cells(data$Q_inzet)
      ex_q2 <- find_empty_cells(data$Q_org)
      ex_q3 <- find_empty_cells(data$Q_pers)
      ex_q4 <- find_empty_cells(data$Q_intent)
      ex_q5 <- find_empty_cells(data$Q_disclosure)
      
      # Create dataframe with NaN's instead of empty
      df = na_in_empty_cells(df)
    }
    return (df)
}

# Make dataframes for each condition
wcA <- make_df(data_A, 'A', 'wc')
infA <- make_df(data_A, 'A', 'inf')
readA <- make_df(data_A, 'A', 'read')
valA <- make_df(data_A, 'A', 'val')
emoA <- make_df(data_A, 'A', 'emo')
demoA <- make_df(data_A, 'A', 'demo')
timeA <- make_df(data_A, 'A', 'time')

wcB <- make_df(data_B, 'B', 'wc')
infB <- make_df(data_B, 'B', 'inf')
readB <- make_df(data_B, 'B', 'read')
valB <- make_df(data_B, 'B', 'val')
emoB <- make_df(data_B, 'B', 'emo')
demoB <- make_df(data_B, 'B', 'demo')
timeB <- make_df(data_B, 'B', 'time')
uxB <- make_df(data_B, 'B', 'ux')

wcC <- make_df(data_C, 'C', 'wc')
infC <- make_df(data_C, 'C', 'inf')
readC <- make_df(data_C, 'C', 'read')
valC <- make_df(data_C, 'C', 'val')
emoC <- make_df(data_C, 'C', 'emo')
demoC <- make_df(data_C, 'C', 'demo')
timeC <- make_df(data_C, 'C', 'time')
uxC <- make_df(data_C, 'C', 'ux')

```

Get the age mean and standard deviation per condition
```{r}
# Get the mean and sd per condition
for (dataset in c('demoA','demoB', 'demoC')){
    data = get(dataset)
    print(dataset)
    print(paste('mean: ', prettyNum(mean(data$dem_age), digits=4)))
    print(paste('sd: ', prettyNum(sd(data$dem_age), digits=4)))
    print('======================================================')

}
# Get the mean and sd for all conditions
print('All')
print(paste('mean: ', prettyNum(mean(c(demoA$dem_age,demoB$dem_age,demoC$dem_age)), digits=4)))
print(paste('sd: ', prettyNum(sd(c(demoA$dem_age,demoB$dem_age,demoC$dem_age)), digits=4)))
```

Make piecharts of Demographic data
```{r}
par(mfrow=c(3,3))
par(mar = c(1, 1, 1, 1))

demo_labels = c('Gender', 'Age','Education')

# Make piecharts for each condition
for (dataset in c('demoA','demoB', 'demoC')){

    # Extract data
    data = get(dataset)
    d_age = data[,1]
    d_gender = data[,2]
    d_edu = data[,3]
    
    # make gender piecharts
    label_list = unique(d_gender)
    count_list = c()
    # transform data to piechart format
    for (label in label_list){
        count_label = length(d_gender[which(d_gender==label)])
        count_list = c(count_list, count_label)
    }
    
    ## Uncomment if you want to print the quantities
    # print('gender counts')
    # print(count_list)
    # print(label_list)
    
    # Create gender piechart
    pie(count_list, labels = label_list)
    title(paste('Gender-', dataset))
    
    # make Age piecharts
    label_list = c('18-34','35-54','55-75')
    count_list = c()
    # Transform data to piechart format
    for (label in label_list){
        low_bound = as.integer(str_sub(label,1,2))
        up_bound = as.integer(str_sub(label,-2,-1))
        count_label = length(d_age[which(d_age>low_bound & d_age<up_bound)])
        count_list = c(count_list, count_label)
      }
    ## Uncomment if you want to print the quantities
    # print('age counts')
    # print(count_list)
    # print(label_list)
    
    # Create age piechart
    pie(count_list, labels = label_list)
    title(paste('Age-', dataset))
    
    #education piecharts
    label_list = c('1-low','2-mid','3-high')
    count_list = c()
    
    # Transform data to piechart format
    for (label in label_list){
      label_i = str_sub(label,1,1)
      count_label = length(grep(label_i, d_edu))
      count_list = c(count_list, count_label)
    }
    ## Uncomment if you want to print the quantities
    # print('education counts')
    # print(count_list)
    # print(label_list)
    
    # create eductation piechart
    pie(count_list, labels = label_list)
    title(paste('Education', dataset))
    
}
```

Visualize main variables in histogram and boxplot of conditions per question
```{r}
# figure parameters
par(mfrow=c(3,5))
par(mar = c(2, 1, 3, 1))

var_names = c('wc', 'inf','read','val','emo')

# Go through each answer measurement
for (var_name in var_names){
  datasets = c()
  
  # create a list of dataset names
  for (i_L in c('A','B','C')){
    data_L = paste(var_name,i_L,sep = '')
    datasets = c(datasets,data_L)
  }
  # get the upperbound for the histograms
  max_data = max(get(datasets[1]),get(datasets[2]), get(datasets[3]), na.rm=TRUE)
  
  # Create histograms of data
  for (dataset in datasets){
    data = get(dataset)
    for (i in c(1:5)){
      # get data
      d_count = data[,i]
      
      # get histogram parameters
      break_num = max(d_count,na.rm=TRUE)
      if (var_name == 'val'){
        break_num = length(unique(c(get(datasets[1]),get(datasets[2]), get(datasets[3]))))
      }
      
      # Make Histogram
      title_plot = paste(dataset,i)
      hist(d_count, breaks = break_num,xlim=c(0, max_data), main = title_plot)
      # place medianline in histogram plot
      abline(v = median(d_count,na.rm=TRUE),col = "blue", lwd = 3)
      # place p-value from Shapiro Wilkis test in plot
      norm_p <- shapiro.test(d_count)
      mtext(prettyNum(norm_p$p.value, digits = 2), side =3, cex = 0.8, line = -2)
    }
  }

  # Make boxplots
  for (dataset in datasets){
    data = get(dataset)
    # go through each question answer
    for (i in c(1:5)){
        # get answer data
        d_count = data[,i]
        title_plot = paste(dataset,i)
        boxplot(d_count,horizontal=TRUE,ylim=c(0,max_data))
        # Place Medianline in boxplot
        abline(v = median(d_count,na.rm=TRUE),col = "blue", lwd = 1)
        title(paste(dataset,i))
    }
}
}

```
Visualize main variables in histogram and boxplot of condition
```{r}
# plots layout parameters
par(mfrow=c(4,3))
par(mar = c(2, 1, 3, 1))

# Go through each variable
var_names = c('wc', 'inf','read','val','emo')
for (var_name in var_names){
  datasets = c()
  
  # get datasets for plots
  for (i_L in c('A','B','C')){
    data_L = paste(var_name,i_L,sep = '')
    datasets = c(datasets,data_L)
  }
  
  # get upperbound for plot 
  max_data = max(get(datasets[1]),get(datasets[2]), get(datasets[3]), na.rm=TRUE)
  for (dataset in datasets){
    data_all = unlist(get(dataset))
    
    # Set histogram breaks
    break_num = max(data_all,na.rm=TRUE)
    # Valence needs a separate break number
    if (var_name == 'val'){
      break_num = length(unique(c(get(datasets[1]),get(datasets[2]), get(datasets[3]))))
    }

    # Make histogram
    title_plot = paste(dataset)
    hist(data_all, breaks = break_num,xlim=c(0,max_data), main = title_plot)
    # Place medianline
    abline(v = median(data_all,na.rm=TRUE),col = "blue", lwd = 3)
    # Place p-value of normality test
    norm_p <- shapiro.test(data_all)
    mtext(prettyNum(norm_p$p.value, digits = 2), side =3, cex = 0.8, line = -2)
    
  }


}

```

Compare question measurements between conditions
```{r}
par(mfrow=c(3,5))

# two-sided Wilcoxon test
get_p <- function(a,b, var_name){

    # Format datastructure
    a = as.numeric(unlist(a))
    b = as.numeric(unlist(b))

    # chisq-test when comparing binary emotions
    # two-sided wilcoxon test otherwise
    if (var_name == 'emo'){
      # format positive, neutral, and negative outcomes of condition a an b
      ca_p1 = length(a[which(a==1)])
      ca_0 = length(a[which(a==0)])
      ca_n1 = length(a[which(a==-1)])
      
      cb_p1 = length(b[which(b==1)])
      cb_0 = length(b[which(b==0)])
      cb_n1 = length(b[which(b==-1)])
      
      matrix_ab <- matrix(c(ca_p1, ca_0, ca_n1,
                            cb_p1, cb_0, cb_n1),
                          nrow = 2, byrow = TRUE)
      twc = chisq.test(matrix_ab)
    }else{
      twc = wilcox.test(a,b, paired = FALSE,na.rm=TRUE)
    }

    # format p-value
    x = prettyNum(twc$p.value, digits = 3)
    # add significance star if below sidak correction
    sidak =  1-(1-0.05)^(1/(3*5))
    if (twc$p.value <= sidak){
      x = paste(toString(format(x, scientific = TRUE)), '*',sep="")
    }
    return (x)
}

# One-sided wilcoxon test
get_p_one_sided <- function(a,b, var_name){

    # Format datastructure
    a = as.numeric(unlist(a))
    b = as.numeric(unlist(b))

    # chisquared test for binary emotional score
    if (var_name == 'emo'){
      # format positive, neutral, and negative outcomes of condition a an b
      ca_p1 = length(a[which(a==1)])
      ca_0 = length(a[which(a==0)])
      ca_n1 = length(a[which(a==-1)])
      
      cb_p1 = length(b[which(b==1)])
      cb_0 = length(b[which(b==0)])
      cb_n1 = length(b[which(b==-1)])
      
      matrix_ab <- matrix(c(ca_p1, ca_0, ca_n1,
                            cb_p1, cb_0, cb_n1),
                          nrow = 2, byrow = TRUE)
      twc = chisq.test(matrix_ab)
    # less or greater wilcoxon test depending on measurement
    }else if (var_name == 'val'){
      twc = wilcox.test(a,b, paired = FALSE,na.rm=TRUE,alternative='less')
    }else{
      twc = wilcox.test(a,b, paired = FALSE,na.rm=TRUE,alternative='greater')
    }
    
    # format p-value
    x = prettyNum(twc$p.value, digits = 3)
    # add star if significance level is below sidak treshold
    sidak =  1-(1-0.1)^(1/(6*5*5))
    if (twc$p.value <= sidak){
      x = paste(toString(format(x, scientific = TRUE)), '*',sep="")
    }
    
    return (x)
}

# Loop through each measurement(variable)
for (var_name in var_names){

    # get dataset for the current variable for each condition
    data_varA = get(paste(var_name,'A',sep = ''))
    data_varB = get(paste(var_name,'B',sep = ''))
    data_varC = get(paste(var_name,'C',sep = ''))
    
    # Go through each question
    for (i in c(1:5)){
      x1 = data_varA[,i]
      x2 = data_varB[,i]
      x3 = data_varC[,i]
      
      # adjust length of dataset with empty  cells
      max_length = max(length(data_varA[,i]),
                       length(data_varB[,i]),
                       length(data_varC[,i]))
      length(x1) <- max_length
      length(x2) <- max_length
      length(x3) <- max_length
      
      # format data to one dataframe
      data_test = data.frame(A = x1,
                             B = x2,
                             C = x3)
      
      # get p-value between each condition pair
      p_list = c()
      p_list_one = c()
      for (c1 in conditions){
        for (c2 in conditions){
          d1 = data_test[c1]
          d2 = data_test[c2]
          
          # two-sided test
          data_p = get_p(d1,d2, var_name)
          # one-sided test
          data_p_one = get_p_one_sided(d1,d2, var_name)
          p_list = c(p_list,data_p)
          p_list_one = c(p_list_one, data_p_one)
          
            
        }
      }
      
      # Print the results into a table
      tab <- matrix(p_list, ncol=3, byrow=TRUE)
      colnames(tab) <- c('A','B','C')
      rownames(tab) <- c('A','B','C')
      tab <- as.table(tab)
      
      tab_one <- matrix(p_list_one, ncol=3, byrow=TRUE)
      colnames(tab_one) <- c('A','B','C')
      rownames(tab_one) <- c('A','B','C')
      tab_one <- as.table(tab_one)
      print(c(var_name, i, 'two-sided'))
      print(tab)
      print('--------\n')
      print(c(var_name, i, 'one-sided'))
      print(tab_one)
      
      print('==================================================\n')
    }
  # }
}  
```
compare all questions combined
```{r}
# two-sided wilcoxon test
get_p <- function(a,b, var_name){
    
    # format datastructure
    a = as.numeric(unlist(a))
    b = as.numeric(unlist(b))

    # chi squared test for emotional score
    # else wilcoxon test
    if (var_name == 'emo'){
      # format positive, neutral, and negative outcomes of condition a an b
      ca_p1 = length(a[which(a==1)])
      ca_0 = length(a[which(a==0)])
      ca_n1 = length(a[which(a==-1)])
      
      cb_p1 = length(b[which(b==1)])
      cb_0 = length(b[which(b==0)])
      cb_n1 = length(b[which(b==-1)])
      
      matrix_ab <- matrix(c(ca_p1, ca_0, ca_n1,
                            cb_p1, cb_0, cb_n1),
                          nrow = 2, byrow = TRUE)
      twc = chisq.test(matrix_ab)
    }else{
      twc = wilcox.test(a,b, paired = FALSE,na.rm=TRUE)
    }
    
    # format p-value
    x = prettyNum(twc$p.value, digits = 3)
    # add * if the p-value is below the p-threshold
    sidak =  1-(1-0.05)^(1/(5))
    if (twc$p.value <= sidak){
      x = paste(toString(format(x, scientific = TRUE)), '*',sep="")
    }
    return (x)
}
#one-sided wilcoxon test
get_p_one_sided <- function(a,b, var_name){

    # print(var_stats$p.value)
    a = as.numeric(unlist(a))
    b = as.numeric(unlist(b))

    if (var_name == 'emo'){
      # format positive, neutral, and negative outcomes of condition a an b
      ca_p1 = length(a[which(a==1)])
      ca_0 = length(a[which(a==0)])
      ca_n1 = length(a[which(a==-1)])
      
      cb_p1 = length(b[which(b==1)])
      cb_0 = length(b[which(b==0)])
      cb_n1 = length(b[which(b==-1)])
      
      matrix_ab <- matrix(c(ca_p1, ca_0, ca_n1,
                            cb_p1, cb_0, cb_n1),
                          nrow = 2, byrow = TRUE)
      twc = chisq.test(matrix_ab)
    }else if (var_name == 'val'){
      twc = wilcox.test(a,b, paired = FALSE,na.rm=TRUE,alternative='less')
    }else{
      twc = wilcox.test(a,b, paired = FALSE,na.rm=TRUE,alternative='greater')
    }
    
    # Format p-value
    x = prettyNum(twc$p.value, digits = 3)
    # add * if p-value is below p-threshold
    sidak =  1-(1-0.1)^(1/(5))
    if (twc$p.value <= sidak){
      x = paste(toString(format(x, scientific = TRUE)), '*',sep="")
    }
    
    return (x)
}

# Go through each measurement/variable
for (var_name in var_names){
    
    # get dataset for the current variable
    data_varA = get(paste(var_name,'A',sep = ''))
    data_varB = get(paste(var_name,'B',sep = ''))
    data_varC = get(paste(var_name,'C',sep = ''))
    
    # format data into one dataframe
    x1 = unlist(as.list(data_varA))
    x2 = unlist(as.list(data_varB))
    x3 = unlist(as.list(data_varC))
    
    max_length = max(length(x1),
                     length(x2),
                     length(x3))
    
    length(x1) <- max_length
    length(x2) <- max_length
    length(x3) <- max_length
    
    data_test = data.frame(A = x1,
                           B = x2,
                           C = x3)
    
    # compare data between each condition pair
    p_list = c()
    p_list_one = c()
    for (c1 in conditions){
      for (c2 in conditions){
        d1 = data_test[c1]
        d2 = data_test[c2]
        
        # two sided test
        data_p = get_p(d1,d2, var_name)
        # one-sided test
        data_p_one = get_p_one_sided(d1,d2, var_name)
        p_list = c(p_list,data_p)
        p_list_one = c(p_list_one, data_p_one)
        
          
      }
    }
    
    # Print the results into a table
    tab <- matrix(p_list, ncol=3, byrow=TRUE)
    colnames(tab) <- c('A','B','C')
    rownames(tab) <- c('A','B','C')
    tab <- as.table(tab)
    
    tab_one <- matrix(p_list_one, ncol=3, byrow=TRUE)
    colnames(tab_one) <- c('A','B','C')
    rownames(tab_one) <- c('A','B','C')
    tab_one <- as.table(tab_one)
    print(c(var_name, 'two-sided'))
    print(tab)
    print('--------\n')
    print(c(var_name, 'one-sided'))
    print(tab_one)
    
    print('==================================================\n')
}
  # }
 
```



Make histograms of the UX and Chatbot experience results
```{r}
# define the UX questions
ux_conds = c('telang', 'formulering', 'saai', 'intuitief','verwarrend', 'nadenkend', 'verkies', 'cb_ervaring', 'cb_survey')
par(mfrow=c(2,2))
par(mar = c(4, 3, 4, 1))

# Go through each question
for (i in c(1:9)){
  # remove na's
  dB <- na.omit(uxB[,i])
  dC <- na.omit(uxC[,i])
  
  # Create histograms for both chatbot conditions
  max_i = max(dB,dC, rm.na=TRUE)
  hist(dB, main=paste(ux_conds[i],'B'), ylim = c(0,30),xlim = c(0,max_i))
  mtext(prettyNum(mean(dB), digits = 2), side =3, cex = 0.8, line = -2)
  hist(dC, main=paste(ux_conds[i],'C'), ylim = c(0,30),xlim = c(0,max_i))
  mtext(prettyNum(mean(dC), digits = 2), side =3, cex = 0.8, line = -2)
  
  
  }
```
ANOVA comparing chatbot vs non-chatboy and speaking vs non-speaking
```{r}
# Go through each variable
for (var_name in var_names){
    
    # get datasets for the variable per condition
    data_varA = get(paste(var_name,'A',sep = ''))
    data_varB = get(paste(var_name,'B',sep = ''))
    data_varC = get(paste(var_name,'C',sep = ''))
    
    # Go through each question
    for (i in c(1:5)){
      # remove any na's
      x1 = log(na.omit(data_varA[,i]))
      x2 = log(na.omit(data_varB[,i]))
      x3 = log(na.omit(data_varC[,i]))
      
      # format data into one dataframe
      max_length = max(length(data_varA[,i]),
                       length(data_varB[,i]),
                       length(data_varC[,i]))
      
      length(x1) <- max_length
      length(x2) <- max_length
      length(x3) <- max_length
      
      df_ABC = data.frame(A = x1,
                          B = x2,
                          C = x3)
      # Compare traditional to chatbot
      ktr_survey = kruskal.test(A ~ interaction(B + C), 
                                data = df_ABC)
      # Compare typing to speaking    
      ktr_speaking = kruskal.test(C ~ interaction(A + B), 
                                data = df_ABC)
      # format p-value
      p_survey = prettyNum(ktr_survey$p.value, digits = 3)
      p_speaking = prettyNum(ktr_speaking$p.value, digits = 3)
      # print results
      print(c(var_name, i))
      print(c('survey: ', p_survey))
      print(c('speaking: ', p_speaking))
      print('-----------------------------------------------')
    }
}

```


Comparing time values
```{r}
# get time data per condition
# objective time condition A
tA = timeA[,3]
# subjective time condition A
tAs = timeA[,4]
tB = timeB[,3]
tBs = timeB[,4]
tC = timeC[,3]
tCs = timeC[,4]

# Remove outlyinng objective times
tAq = quantile(tA, 0.95,na.rm = TRUE )
tBq = quantile(tB, 0.95,na.rm = TRUE )
tCq = quantile(tC, 0.95,na.rm = TRUE )

ex_tA = which(tA>tAq)
ex_tB = which(tB>tBq)
ex_tC = which(tC>tCq)

tA <- tA[-c(ex_tA)]
tAs <- tAs[-c(ex_tA)]
tB <- tB[-c(ex_tB)]
tBs <- tBs[-c(ex_tB)]
tC <- tC[-c(ex_tC)]
tCs <- tCs[-c(ex_tC)]

# print objective and subjective times next to eachother
print('Actual time vs subjective times; Averages')             
print(paste(prettyNum(mean(tA, na.rm= TRUE), digits = 3),'-',
            prettyNum(mean(tAs, na.rm= TRUE), digits= 3)))
print(paste(prettyNum(mean(tB, na.rm= TRUE), digits = 3),'-',
            prettyNum(mean(tBs, na.rm= TRUE), digits= 3)))
print(paste(prettyNum(mean(tC, na.rm= TRUE), digits = 3),'-',
            prettyNum(mean(tCs, na.rm= TRUE), digits= 3)))

# combine times
real_times = c('tA','tB','tC')
subj_times = c('tAs','tBs','tCs')

# Check for normal distribution
# With log most are still non-normally distributed
for (t_var in c('tA','tAs','tB','tBs','tC','tCs')){
  x = shapiro.test(get(t_var))
  print(paste(t_var,': ',prettyNum(x$p.value, digits=3)))
}

# Two sided wilcoxon test
tA_wt = wilcox.test(tA, tAs, paired=TRUE, na.rm=TRUE)
tB_wt = wilcox.test(tB, tBs, paired=TRUE, na.rm=TRUE)
tC_wt = wilcox.test(tC, tCs, paired=TRUE, na.rm=TRUE)
# one-sided wilcoxon test
# Typing condition, only check if objective time is lower
tA_wto = wilcox.test(tA, tAs, paired=TRUE, na.rm=TRUE, alternative='less')
# Chatbot conditions, only check if objective time is larger
tB_wto = wilcox.test(tB, tBs, paired=TRUE, na.rm=TRUE, alternative='greater')
tC_wto = wilcox.test(tC, tCs, paired=TRUE, na.rm=TRUE, alternative='greater')


# Print two-sided test results
print("two-sided")
print(paste('tA-tAs: ',prettyNum(tA_wt$p.value, digits=3)))
print(paste('tB-tBs: ',prettyNum(tB_wt$p.value, digits=3)))
print(paste('tC-tCs: ',prettyNum(tC_wt$p.value, digits=3)))

# print one-sided test results
print("One-sided")
print(paste('tA-tAs: ',prettyNum(tA_wto$p.value, digits=3)))
print(paste('tB-tBs: ',prettyNum(tB_wto$p.value, digits=3)))
print(paste('tC-tCs: ',prettyNum(tC_wto$p.value, digits=3)))



```
Compare objective time and subjective time with sidak correction
```{r}

get_p_time <- function(twc){
    x = prettyNum(twc$p.value, digits = 3)
    # add * if p-value is below p-threshold
    sidak =  1-(1-0.1)^(1/(3))
    if (twc$p.value <= sidak){
      x = paste(toString(format(x, scientific = TRUE)), '*',sep="")
    }
    return (x)
}

print(paste('O:tA-tAs: ',get_p_time(tA_wto)))
print(paste('O:tB-tBs: ',get_p_time(tB_wto)))
print(paste('O:tC-tCs: ',get_p_time(tC_wto)))
```
Write timedata to a csv for easier overview
```{r}
# Format timedata to one dataframe
max_length = max(length(tA), length(tAs),
                 length(tB), length(tBs),
                 length(tC), length(tCs))
      
length(tA) <- max_length
length(tB) <- max_length
length(tC) <- max_length

length(tAs) <- max_length
length(tBs) <- max_length
length(tCs) <- max_length


time_data_df <- data.frame(tA, tB, tC, tAs, tBs, tCs)

# write time dataframe to csv
write.csv(time_data_df, "D:\\VU\\Validators\\Data\\time_data.csv", row.names=FALSE)



```

